---
title: "Presentation Title"
subtitle: "Subtitle or one-line description"
author: "Author Name"
institute: DECDI, The World Bank
date: today
format:
  decdi-revealjs:
    output-file: index.html
    toc: true
    toc-depth: 1
    toc-location: body
    toc-title: "Contents"
    self-contained: true
    logo: "_extensions/decdi/logos/COLOR_WB_DEC.png"
    footer: "DECDI | [Your Program Name]"
---

```{r Setup}
#| include: false
source("_extensions/decdi/setup_decdi_palettes.R")
source("_extensions/decdi/setup_ggplot2_decdi.R")

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, ggplot2, gt, knitr)
```

## Agenda

- Context / motivation
- Approach
- Results
- Next steps

# Context {background-color="#002A4F"}

## Context slide

One idea per slide. Keep bullets short — this is a talking prompt, not a
document.

- Point one
- Point two
- Point three

# Results {background-color="#002A4F"}

## A figure

```{r}
#| echo: false
#| fig.align: center
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(color = decdi_palette("DECDI")["BlueMid"]) +
  labs(title = "Figure Title", x = "X axis label", y = "Y axis label")
```

::: {.visual-note}
**Notes:** Points show individual observations. Add a source line here only if
the visual uses an external source.
:::

## A table

```{r}
#| echo: false
mtcars |>
  dplyr::slice_head(n = 5) |>
  dplyr::select(mpg, cyl, wt) |>
  gt::gt() |>
  gt::tab_header(title = "Table Title")
```

::: {.visual-note}
**Notes:** Add significance, uncertainty, sample, units, or restrictions only
when they are needed for interpretation.
:::

# Next Steps {background-color="#002A4F"}

## Next steps

- Action item one
- Action item two

## Thank you

Questions / discussion.
