---
title: "Presentation Title"
subtitle: "Subtitle or one-line description"
author: "Author Name"
institute: DECDI, The World Bank
date: today
format:
  decdi-revealjs:
    output-file: index.html
    toc: true
    toc-depth: 1
    toc-location: body
    toc-title: "Contents"
    self-contained: true
    logo: "_extensions/decdi/logos/COLOR_WB_DEC.png"
    footer: "DECDI | [Your Program Name]"
---

```{r Setup}
#| include: false
source("_extensions/decdi/setup_decdi_palettes.R")
source("_extensions/decdi/setup_ggplot2_decdi.R")

required_pkgs <- c("dplyr", "ggplot2", "gt", "knitr")
missing_pkgs <- required_pkgs[!vapply(required_pkgs, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing_pkgs)) stop("Missing R packages: ", paste(missing_pkgs, collapse = ", "), ". Install them before rendering.")
invisible(lapply(required_pkgs, library, character.only = TRUE))
```

## Agenda

- Context / motivation
- Approach
- Results
- Next steps

# Context {background-color="#002A4F"}

## Context slide

One idea per slide. Keep bullets short — this is a talking prompt, not a
document.

- Point one
- Point two
- Point three

# Results {background-color="#002A4F"}

## One visual

<!-- Pattern: one-visual. Keep only the title, visual, and necessary note. -->

```{r}
#| echo: false
#| fig.align: center
#| fig-width: 11
#| fig-height: 5
#| out-width: 100%
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(color = decdi_palette("DECDI")["BlueMid"]) +
  labs(x = "Vehicle weight", y = "Fuel economy")
```

::: {.visual-note}
**Notes:** Points show individual observations. Add a source line here only if
the visual uses an external source.
:::

## Visual and text

<!-- Pattern: visual-and-text. Keep visible prose to three bullets or about 45 words. -->

:::: {.columns}

::: {.column width="50%"}

- Fuel economy declines as vehicle weight rises.
- The pattern is visible across the sample.
- Use the note for qualifications the audience needs.

:::

::: {.column width="50%"}

```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 4.5
#| out-width: 100%
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(color = decdi_palette("DECDI")["BlueMid"]) +
  labs(x = "Vehicle weight", y = "Fuel economy")
```

:::

::::

## Comparison

<!-- Pattern: comparison. Use exactly two equal visual areas. -->

:::: {.columns}

::: {.column width="50%"}

### Four-cylinder vehicles

```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 4
#| out-width: 100%
mtcars |>
  dplyr::filter(cyl == 4) |>
  ggplot(aes(wt, mpg)) +
  geom_point(color = decdi_palette("DECDI")["BlueMid"]) +
  labs(x = "Vehicle weight", y = "Fuel economy")
```

:::

::: {.column width="50%"}

### Six- and eight-cylinder vehicles

```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 4
#| out-width: 100%
mtcars |>
  dplyr::filter(cyl != 4) |>
  ggplot(aes(wt, mpg)) +
  geom_point(color = decdi_palette("DECDI")["Navy"]) +
  labs(x = "Vehicle weight", y = "Fuel economy")
```

:::

::::

## A table

```{r}
#| echo: false
mtcars |>
  dplyr::slice_head(n = 5) |>
  dplyr::select(mpg, cyl, wt) |>
  gt::gt() |>
  gt::tab_header(title = "Table Title")
```

::: {.visual-note}
**Notes:** Add significance, uncertainty, sample, units, or restrictions only
when they are needed for interpretation.
:::

# Next Steps {background-color="#002A4F"}

## Next steps

- Action item one
- Action item two

## Thank you

Questions / discussion.
